Efficiency

### 2018-02-11 DraftExec.Rnw
latest

Having done my higher education in physics, and spent considerable time considering military maritime technology running a small start-up defence company I found seemingly unresolved series of exchanges regarding the pumpjet choice particulaly curious.  As is commonly quipped, including in defence circles, it can be reliably assumed when it comes to technology choices ``there's no free lunch in physics".  Whilst all technologies steadily improve, and new ones continuously emerge, it's inevitably the case that when significant technology switches are made, some trade-offs are necessary. In the case of the pumpjets, the trade-offs what might have been expected appeared obvious, and probably unavoidable to some extent to all those experienced in maritime systems: it would have lower propulsive efficiency, particularly at low speeds.

>>>>

Having done my higher education in physics, and spent considerable time considering military maritime technology running a small start-up defence company I found seemingly unresolved series of exchanges regarding the pumpjet choice particulaly curious.  As is commonly quipped, including in defence circles, it can be reliably assumed when it comes to technology choices ``there's no free lunch in physics".  Whilst all technologies steadily improve, and new ones continuously emerge, it's inevitably the case that when significant technology switches are made, some trade-offs are necessary. In the case of the pumpjets, the trade-offs that might have been expected appeared obvious, and probably unavoidable to some extent to all those experienced in maritime systems: it would have lower propulsive efficiency, particularly at low speeds.
